#Repdata-005 Peer Assessment 1

## Load data
```{r loaddata}
fileUrl <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = "activity.zip")

unzip(zipfile="activity.zip")
activitydata <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
## Excluding NAs
total.steps <- tapply(activitydata$steps, activitydata$date, FUN=sum, na.rm=TRUE)
qplot(total.steps, binwidth=1000, xlab="Total No. of Steps Taken Each Day")
mean(total.steps, na.rm=TRUE)
median(total.steps, na.rm=TRUE)
```

## The average daily activity pattern
```{r}
library(ggplot2)
## Excluding NAs
averages <- aggregate(x=list(steps=activitydata$steps), by=list(interval=activitydata$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(activitydata=averages, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-min interval") +
    ylab("Avg No. of Steps Taken")
```

On average across all the days in the dataset, the 5-minute interval contains
the max no. of steps
```{r}
averages[which.max(averages$steps),]
```

## Imputing missing values

```{r how_many_missing}
missing <- is.na(activitydata$steps)
# How many missing ( get both missing and available records)
table(missing)
```

Approach: Set all of the missing values are filled in with the MEAN value for that 5-minute
interval.

```{r}
# Replace each missing value with the mean value of its 5-minute interval
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (averages[averages$interval==interval, "steps"])
    return(filled)
}
filled.activitydata <- activitydata
filled.activitydata$steps <- mapply(fill.value, filled.activitydata$steps, filled.activitydata$interval)
```
Create a histogram of the total no. of steps taken each day and calculate the mean and median total number of steps.

```{r}
total.steps <- tapply(filled.activitydata$steps, filled.activitydata$date, FUN=sum)
qplot(total.steps, binwidth=1000, xlab="Total No. of Steps Taken Each Day")
mean(total.steps)
median(total.steps)
```



##Differences in activity patterns between weekdays and weekends



```{r}
weekday.or.weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
filled.activitydata$date <- as.Date(filled.activitydata$date)
filled.activitydata$day <- sapply(filled.activitydata$date, FUN=weekday.or.weekend)
```

Create a panel plot containing plots of average number of steps taken
on weekdays and weekends.
```{r}
averages <- aggregate(steps ~ interval + day, activitydata=filled.activitydata, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-min interval") + ylab("No. of steps")