averages <- aggregate(steps ~ interval + day, data=filled.data, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-min interval") + ylab("No. of steps")



steps_by_time_and_weektime = with(data, aggregate(x=steps, by=list(interval, weektime), 
                                                  FUN=function(x) mean(x, na.rm=T)))
names(steps_by_time_and_weektime) = c("Time", "Weektime", "Mean.Steps")
xyplot(Mean.Steps ~ Time | Weektime, data=steps_by_time_and_weektime, layout=c(1,2), type='l')





#Repdata-005 Peer Assessment 1

## Load data
```{r loaddata}
fileUrl <- "http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = "activity.zip")

unzip(zipfile="activity.zip")
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
library(lattice)
## Excluding NAs
total.steps <- tapply(data$steps, data$date, FUN=sum, na.rm=TRUE)
qplot(total.steps, binwidth=1000, xlab="Total No. of Steps Taken Each Day")
mean(total.steps, na.rm=TRUE)
median(total.steps, na.rm=TRUE)
```

## The average daily activity pattern
```{r}

## Excluding NAs
averages <- aggregate(x=list(steps=data$steps), by=list(interval=data$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(data=averages, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-min interval") +
    ylab("Avg No. of Steps Taken")
```

On average across all the days in the dataset, the 5-minute interval contains
the max no. of steps
```{r}
averages[which.max(averages$steps),]
```

## Imputing missing values

```{r how_many_missing}
missing <- is.na(data$steps)
# How many missing ( get both missing and available records)
table(missing)
```

Approach: Set all of the missing values are filled in with the MEAN value for that 5-minute
interval.

```{r}
# Replace each missing value with the mean value of its 5-minute interval
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (averages[averages$interval==interval, "steps"])
    return(filled)
}
filled.data <- data
filled.data$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)
```
Create a histogram of the total no. of steps taken each day and calculate the mean and median total number of steps.

```{r}
total.steps <- tapply(filled.data$steps, filled.data$date, FUN=sum)
qplot(total.steps, binwidth=1000, xlab="Total No. of Steps Taken Each Day")
mean(total.steps)
median(total.steps)
```



##Differences in activity patterns between weekdays and weekends



```{r}
data$weekday = weekdays( as.Date(data$date) )
weekends = (data$weekday == 'Saturday' | data$weekday == 'Sunday')

data$weektime = 'weekend'
data[!weekends,]$weektime = 'weekday'

data$weektime = as.factor(data$weektime)

```

Create a panel plot containing plots of average number of steps taken
on weekdays and weekends.
```{r}

steps_by_time_and_weektime = with(data, aggregate(x=steps, by=list(interval, weektime), 
                                                  FUN=function(x) mean(x, na.rm=T)))
names(steps_by_time_and_weektime) = c("Time", "Weektime", "Mean.Steps")
xyplot(Mean.Steps ~ Time | Weektime, data=steps_by_time_and_weektime, layout=c(1,2), type='l')




